---
title: "Recommendation System"
author: "Murilo Miranda"
date: "2/21/2020"
output:
  html_document:
    toc: true # table of content true
    toc_float: true
    code_folding: hide
    toc_depth: 2  # upto three depths of headings (specified by #, ## and ###)
    theme: united
    highlight: breezedark  # specifies the syntax highlighting style
    #css: styles.css
  pdf_document: default
version: '0.3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits = 5, scipen=999)
```


```{r, message=FALSE}
library(RMySQL)
library(ggpubr)
library(tidyverse)
library(stringr)
library(lubridate)
library(recommenderlab)
library(arules)
library(arulesViz)
library(cluster)
library(factoextra)
library(knitr)
```

```{r, echo=FALSE}
db_password <- 'Danielly1964'
```

We want to build a **recommendation system** to increase cross-selling in our website. Our goal is to show customers who have added a product to their basket another product they’re likely to want. Because of the nature of our data, the best way to do that is by using a method called **Market Basket Analysis**.

The first step is the **data quality** assessment: we need to make sure that we can trust the data that we’re using. Make sure the information across our datasets (_line_item_, _orders_ and _products_) is consistent, and get rid of anything too strange or to believe.

Then, we will have to build a **transactional dataset**: a table with one row per order and one column per product bought -meaning that the table has as many columns as the biggest order, with lots of NAs.

Finally, we will use the **apriori algorithm** to create if-then rule with our products: “if a customer buys product A, then it’s likely that they’ll buy product B”. Focus on optimizing the model: it will be deployed into production by our engineering team. 


### Read data from mySQL
```{r, message=FALSE}
mydb <-  dbConnect(MySQL(), user = 'root', password = db_password,
                 dbname = 'imarket_sql', host = '127.0.0.1', port = 3306)
rm(db_password)
```

#### import line_item table
```{r, results='hide'}
rs <- dbSendQuery(mydb, "select * from line_item")
line_item <-  fetch(rs, n = -1)
dbClearResult(rs)
```

#### import orders table
```{r, results='hide'}
rs <- dbSendQuery(mydb, "select * from orders")
orders <-  fetch(rs, n = -1)
dbClearResult(rs)
```

#### import products table
```{r, results='hide'}
rs <- dbSendQuery(mydb, "select * from products")
products <-  fetch(rs, n = -1)
dbClearResult(rs)
on.exit(dbDisconnect(mydb))
```

## Data Quality

1. Check that all **orders** in _line_item_ are present in our _orders_ dataset. Exclude from _line_item_ any rows that do not meet that condition.

```{r, warning=FALSE}
line_item <- line_item %>% mutate(date = ymd_hms(date), unit_price = as.numeric(gsub(",", ".", unit_price)))

orders <- orders %>% mutate(created_date = ymd_hms(created_date), total_paid = as.numeric(gsub(",", ".", total_paid)))

products <- products %>% mutate(price = as.numeric(as.character(price)))
#mutate(price = str_replace(price, "90{2,}.+", "9")) %>%

line_item_clean <- line_item %>% inner_join(orders, by = "id_order")
```

2. Exclude from _line_item_ any rows from orders that are not **“Completed”**.

```{r}
line_item_clean <- line_item_clean %>% filter(state == "Completed") %>% select(-state, -product_id)
```

3. Check that all **products** in _line_item_ are present in the _products_ dataset. Exclude from _line_item_ any rows that do not meet that condition.

```{r}
line_item_clean <- line_item_clean %>% filter(sku %in% products$sku)
```

4. Explore the relationship between **prices** in _line_item_ and _order_.

```{r}
values_paid <- line_item_clean %>% group_by(id_order) %>% 
  summarise(total_estimated = sum(unit_price*product_quantity), total_paid = mean(total_paid))

values_paid %>% 
  ggplot(aes(x = total_estimated, y = total_paid)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "SUM(unit price * product quantity)",
    y = "total paid"
  )
```

  a. Do the prices of the orders and the sum of the prices of each item in the order match? If not, can you make some assumptions that explain the differences?

>**No, some orders had more than one product and probably the total paid includes shipping and other taxes.**

  b. Exclude from _line_items_ the rows with differences that you cannot explain.

```{r}
values_paid <- values_paid %>% filter(abs(total_estimated - total_paid) < total_paid*0.50)

line_item_clean <- line_item_clean %>% filter(id_order %in% values_paid$id_order)
rm(values_paid)
```

```{r,echo=FALSE}
line_item_clean %>% group_by(id_order) %>% 
  summarise(total_estimated = sum(unit_price*product_quantity), total_paid = mean(total_paid)) %>% 
  ggplot(aes(x = total_estimated, y = total_paid)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "SUM(unit price * product quantity)",
    y = "total paid"
  )
```

5. Explore the relationship between **prices** in _line_item_ and _product_:

```{r}
line_item_clean <- line_item_clean %>% inner_join(products, by = "sku")
```

```{r}
line_item_clean %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

  a. Do the prices of the items sold and the product prices match? If not, can you make some assumptions that explain the differences?
  
>**No, kmeans algorithm identified four groups. Some of these groups were divided into subgroups. Groups/Subgroups were transformed by x-values**
  
```{r, warning=FALSE}
set.seed(1605)

# function to compute total within-cluster sum of square 
wss <- function(k) {
  kmeans(line_item_clean[, c("price", "unit_price")], k, nstart = 10 )$tot.withinss
}

# Compute and plot wss for k = 2 to k = 15
k.values <- 2:15

# extract wss for 2-15 clusters
wss_values <- map_dbl(k.values, wss)

plot(k.values, log10(wss_values),
       type="b", pch = 19, frame = FALSE, 
       xlab="Number of clusters K",
       ylab="log10(Total within-clusters sum of squares)")
```

```{r}
k4 <- kmeans(line_item_clean[, c("price", "unit_price")], centers = 4, nstart = 10)
fviz_cluster(k4, data = line_item_clean[, c("price", "unit_price")])
```

##### Group 1
```{r}
line_item_group1 <- line_item_clean %>% filter(k4$cluster == 1)

g_before <- line_item_group1 %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

###### Group 1a
```{r group1a}
line_item_group1a <- line_item_group1 %>% filter(price/unit_price > 30000)
```

```{r, include=FALSE}
line_item_group1a %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

```{r}
line_item_group1a %>% select(unit_price, price) %>% summary()
line_item_group1a <- line_item_group1a %>% mutate(price = price/100000)
```

###### Group 1b
```{r group1b}
line_item_group1b <- line_item_group1 %>% filter(price/unit_price < 30000)
```

```{r, include=FALSE}
line_item_group1b %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

```{r}
line_item_group1b %>% select(unit_price, price) %>% summary()
line_item_group1b <- line_item_group1b %>% mutate(price = price/10000)
```

```{r}
line_item_group1 <- line_item_group1a %>% bind_rows(line_item_group1b)

g_after <- line_item_group1 %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )

rm(line_item_group1a, line_item_group1b)
```

```{r}
ggarrange(g_before, g_after, labels = c("Before", "After"), ncol = 2, nrow = 1)
```

##### Group 2
```{r}
line_item_group2 <- line_item_clean %>% filter(k4$cluster == 2)

g_before <- line_item_group2 %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

###### Group 2a
```{r group4a}
line_item_group2a <- line_item_group2 %>% filter(price/unit_price > 20000)
```

```{r, include=FALSE}
line_item_group2a %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

```{r}
line_item_group2a %>% select(unit_price, price) %>% summary()
line_item_group2a <- line_item_group2a %>% mutate(price = price/100000)
```

###### Group 2b
```{r group2b}
line_item_group2b <- line_item_group2 %>% filter(price/unit_price < 20000)
```

```{r, include=FALSE}
line_item_group2b %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

```{r}
line_item_group2b %>% select(unit_price, price) %>% summary()
line_item_group2b <- line_item_group2b %>% mutate(price = price/10000)
```

```{r}
line_item_group2 <- line_item_group2a %>% bind_rows(line_item_group2b)

g_after <- line_item_group2 %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )

rm(line_item_group2a, line_item_group2b)
```

```{r}
ggarrange(g_before, g_after, labels = c("Before", "After"), ncol = 2, nrow = 1)
```

##### Group 3
```{r}
line_item_group3 <- line_item_clean %>% filter(k4$cluster == 3)

g_before <- line_item_group3 %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

```{r}
set.seed(1605)
k2 <- kmeans(line_item_group3[, c("price", "unit_price")], centers = 2, nstart = 10)
```

###### Group 3a
```{r group3a}
line_item_group3a <- line_item_group3 %>% filter(k2$cluster == 1)
```

```{r, include=FALSE}
line_item_group3a %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

There two subgroups: (1) unit price higher than 1000 and price smaller than 7000 (group3aSmall) and (2) unit price smaller than 1000 and price higher than 7000 (group3aHigh)

```{r group3aSmall}
line_item_group3aSmall <- line_item_group3a %>% filter((price-5000)/unit_price < 50)
```

```{r, include=FALSE}
line_item_group3aSmall %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

The group3aSmall was kept.

```{r group3aHigh}
line_item_group3aHigh <- line_item_group3a %>% filter((price-5000)/unit_price >= 50)
```

```{r, include=FALSE}
line_item_group3aHigh %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

The group3aHigh also has two subgroup: (1) ratio price and unit_price higher than 4000 (higher) and (2) ratio price and unit_price smaller than 4000 (smaller).

```{r higher}
line_item_higher <- line_item_group3aHigh %>% filter(price/unit_price > 4000)
```

```{r, include=FALSE}
line_item_higher %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

```{r}
line_item_higher %>% select(unit_price, price) %>% summary()
line_item_higher <- line_item_higher %>% mutate(price = price/10000)
```

```{r smaller}
line_item_smaller <- line_item_group3aHigh %>% filter(price/unit_price < 4000)
```

```{r, include=FALSE}
line_item_smaller %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

```{r}
line_item_smaller %>% select(unit_price, price) %>% summary()
line_item_smaller <- line_item_smaller %>% mutate(price = price/1000)
```

```{r}
line_item_group3aHigh <- line_item_higher %>% bind_rows(line_item_smaller)
line_item_group3a <- line_item_group3aSmall %>% bind_rows(line_item_group3aHigh)

rm(line_item_higher, line_item_smaller, line_item_group3aSmall, line_item_group3aHigh)
```

###### Group 3b
```{r group3b}
line_item_group3b <- line_item_group3 %>% filter(k2$cluster == 2)
```

```{r,include=FALSE}
line_item_group3b %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

There two subgroups: (1) unit price smaller than 400 (group3bSmall) and (2) higher than 400 (group3bHigh)

```{r group3bSmall}
line_item_group3bSmall <- line_item_group3b %>% filter(unit_price < 400)
```

```{r,include=FALSE}
line_item_group3bSmall %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

The group3bSmall was divided by 10000.
```{r}
line_item_group3bSmall %>% select(unit_price, price) %>% summary()
line_item_group3bSmall <- line_item_group3bSmall %>% mutate(price = price/10000)
```

```{r group3bHigh}
line_item_group3bHigh <- line_item_group3b %>% filter(unit_price > 400)
```

```{r, include=FALSE}
line_item_group3bHigh %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

The group3bHigh was divided by 1000.
```{r}
line_item_group3bHigh %>% select(unit_price, price) %>% summary()
line_item_group3bHigh <- line_item_group3bHigh %>% mutate(price = price/1000)
```

```{r}
line_item_group3b <- line_item_group3bSmall %>% bind_rows(line_item_group3bHigh)
line_item_group3 <- line_item_group3a %>% bind_rows(line_item_group3b)

g_after <- line_item_group3 %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )

rm(line_item_group3bSmall, line_item_group3bHigh, line_item_group3a, line_item_group3b)
```

```{r}
ggarrange(g_before, g_after, labels = c("Before", "After"), ncol = 2, nrow = 1)
```

##### Group 4
```{r}
line_item_group4 <- line_item_clean %>% filter(k4$cluster == 4)

g_before <- line_item_group4 %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1, slope = 20000) +
  labs(
    x = "unit price",
    y = "price"
  )
```

```{r}
line_item_group4 %>% select(unit_price, price) %>% summary()
line_item_group4 <- line_item_group4 %>% mutate(price = price/100000)
```

```{r}
g_after <- line_item_group4 %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1, slope = 20000) +
  labs(
    x = "unit price",
    y = "price"
  )
```

```{r}
ggarrange(g_before, g_after, labels = c("Before", "After"), ncol = 2, nrow = 1)
```

##### All groups
```{r}
g_before <- line_item_clean %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1, slope = 20000) +
  labs(
    x = "unit price",
    y = "price"
  )

line_item_clean <- line_item_group1 %>% bind_rows(line_item_group2) %>% bind_rows(line_item_group3) %>% bind_rows(line_item_group4)

g_after <- line_item_clean %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )

rm(line_item_group1, line_item_group2, line_item_group3, line_item_group4)
```

```{r}
ggarrange(g_before, g_after, labels = c("Before", "After"), ncol = 2, nrow = 1)
```

  b. Exclude from _line_items_ the rows with differences that you cannot explain.

>**For now, we decided to keep only the values which the absolute difference between unit price and price is smaller than the price multiplied by 75%**

```{r}
line_item_clean <- line_item_clean %>% filter(abs(unit_price - price) < price*0.75)
```

```{r}
line_item_clean %>% ggplot(aes(unit_price, price)) + 
  geom_point() + 
  geom_abline(colour = 'red', size = 1.1) +
  labs(
    x = "unit price",
    y = "price"
  )
```

```{r}
rm(g_after, g_before, k2, k4, k.values, wss_values)
```

## Transactional Dataset

```{r}
# Due to limitation process some sku-items with low frequency (< 3 times bought) were removed
product_freq <- line_item_clean %>% group_by(sku) %>% summarise(quantity = sum(product_quantity)) %>% filter(quantity >= 3)

line_item_clean <- line_item_clean %>% filter(sku %in% product_freq$sku)

transact <- line_item_clean %>% arrange(id_order) %>% mutate(id_order_sku = paste(id_order, sku, sep = ";")) %>% select(id_order_sku) %>% unlist(., use.names=FALSE) %>% paste(., collapse = "\n" )

paste("item_id;trans_id", transact, sep = "\n") %>% write("item_list")
rm(product_freq)
```

```{r}
transact <- read.transactions("item_list", format = "single", header = TRUE, sep = ";", cols = c("item_id", "trans_id"))
summary(transact)
```

```{r}
itemFrequencyPlot(transact, type = "absolute", horiz= TRUE, top = 20, support = 0.005, cex.names = .5)
```

## Apriori Algorithm

#### Choice of support and confidence
```{r, message=FALSE, results='hide'}
# Support and confidence values
supportLevels <- c(0.01, 0.005, 0.001, 0.0005, 0.0001)
confidenceLevels <- c(0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1)

# Empty integers 
rules_supA <- integer(length=9)
rules_supB <- integer(length=9)
rules_supC <- integer(length=9)
rules_supD <- integer(length=9)
rules_supE <- integer(length=9)

for (i in 1:length(confidenceLevels)) {
  # Apriori algorithm with a support level of 1%
  rules_supA[i] <- length(apriori(transact, parameter=list(sup=supportLevels[1], 
                                  conf=confidenceLevels[i], target="rules", 
                                  minlen = 2)))
  
  # Apriori algorithm with a support level of 0.5%
  rules_supB[i] <- length(apriori(transact, parameter=list(sup=supportLevels[2], 
                                  conf=confidenceLevels[i], target="rules", 
                                  minlen = 2)))
  
  # Apriori algorithm with a support level of 0.1%
  rules_supC[i] <- length(apriori(transact, parameter=list(sup=supportLevels[3], 
                                  conf=confidenceLevels[i], target="rules", 
                                  minlen = 2)))
  
  # Apriori algorithm with a support level of 0.05%
  rules_supD[i] <- length(apriori(transact, parameter=list(sup=supportLevels[4], 
                                  conf=confidenceLevels[i], target="rules", 
                                  minlen = 2)))
  
  # Apriori algorithm with a support level of 0.01%
  rules_supE[i] <- length(apriori(transact, parameter=list(sup=supportLevels[5], 
                                  conf=confidenceLevels[i], target="rules", 
                                  minlen = 2)))
}
```

```{r}
# Data frame
num_rules <- data.frame(rules_supA, rules_supB, rules_supC, rules_supD, rules_supE, confidenceLevels)

# Number of rules found with a support level of 1%, 0.5%, 0.1%, 0.05% and 0.01%
ggplot(data=num_rules, aes(x=confidenceLevels)) +
  
  # Plot line and points (support level of 1%)
  geom_line(aes(y=rules_supA, colour="Support level of 1%")) + 
  geom_point(aes(y=rules_supA, colour="Support level of 1%")) +
  
  # Plot line and points (support level of 0.5%)
  geom_line(aes(y=rules_supB, colour="Support level of 0.5%")) +
  geom_point(aes(y=rules_supB, colour="Support level of 0.5%")) +
  
  # Plot line and points (support level of 0.1%)
  geom_line(aes(y=rules_supC, colour="Support level of 0.1%")) + 
  geom_point(aes(y=rules_supC, colour="Support level of 0.1%")) +
  
  # Plot line and points (support level of 0.05%)
  geom_line(aes(y=rules_supD, colour="Support level of 0.05%")) +
  geom_point(aes(y=rules_supD, colour="Support level of 0.05%")) +
  
  # Plot line and points (support level of 0.01%)
  geom_line(aes(y=rules_supE, colour="Support level of 0.01%")) +
  geom_point(aes(y=rules_supE, colour="Support level of 0.01%")) +
  
  # Labs and theme
  labs(x="Confidence levels", y="Number of rules found", 
       title="Apriori algorithm with different support levels") +
  theme_bw() +
  theme(legend.title=element_blank())
rm(i, rules_supA, rules_supB, rules_supC, rules_supD, rules_supE, confidenceLevels, supportLevels, num_rules)
```

#### Decision
We decided to use 0.01% for support and 50% confidence.

```{r, results='hide'}
trans_rules <- apriori(transact, parameter = list(support = 0.0001, confidence = 0.5, minlen = 2)) 
```

```{r}
summary(trans_rules)
```

```{r}
inspectDT(trans_rules)
```

```{r, fig.height=10}
plot(trans_rules, method = "grouped")
```

```{r, fig.height=10}
plot(trans_rules, method = "graph", engine = "htmlwidget")
```

```{r, results='hide', echo=FALSE}
# fsets <- eclat(transact, parameter = list(support = 0.00023), control = list(verbose=FALSE))
# singleItems <- fsets[size(items(fsets)) == 1]
# singleSupport <- quality(singleItems)$support
# names(singleSupport) <- unlist(LIST(items(singleItems), decode = FALSE))
# head(singleSupport, n = 5)
# itemsetList <- LIST(items(fsets), decode = FALSE)
# allConfidence <- quality(fsets)$support / sapply(itemsetList, function(x) max(singleSupport[as.character(x)]))
# 
# quality(fsets) <- cbind(quality(fsets), allConfidence)
# summary(fsets)
```

```{r, echo=FALSE, results='asis'}
products_id <- unique(c(unlist(LIST(rhs(trans_rules))), unlist(LIST(lhs(trans_rules)))))

kable(line_item_clean %>% filter(sku %in% products_id) %>% select(sku, name_en, short_desc_en, brand, manual_categories) %>% rename(Name = name_en, Description = short_desc_en, Brand = brand, Category = manual_categories) %>% unique() %>% arrange(sku))
rm(products_id)
```

#### Building a recommendation system
```{r}
# Create unique identifier
line_item_clean <- line_item_clean %>% mutate(order_sku = paste(id_order, sku, sep = ' '))

# Filter out duplicates and drop unique identifier
line_item_clean <- line_item_clean[!duplicated(line_item_clean$order_sku), ] %>% select(-order_sku)
```

```{r}
order_item_matrix <- line_item_clean %>%
# Select only needed variables
  select(id_order, sku) %>% 
# Add a column of 1s
  mutate(value = 1) %>%
# Spread into order-item format
  spread(sku, value, fill = 0) %>%
  select(-id_order) %>%
# Convert to matrix
  as.matrix() %>%
# Convert to recommenderlab class 'binaryRatingsMatrix'
  as("binaryRatingMatrix")
```

The data was split into a train and a test set by selecting train = 0.8 for a 80/20 train/test split. The method was set “cross” up with 2-fold cross validation. This means that the data is divided into 2 subsets of equal size, with 80% of the data used for training and the remaining 20% used for evaluation. The models are recursively estimated 2 times, each time using a different train/test split, which ensures that all orders and items are considered for both training and testing. The results can then be averaged to produce a single evaluation set. Selecting given = -1 means that for the test orders ‘all but 1’ randomly selected item is withheld for evaluation.

```{r, warning=FALSE}
# split the data into the training and the test set
transact_rs <- evaluationScheme(order_item_matrix, method = "cross", k = 1, train = 0.8, given = -1)

transact_rs
```

```{r}
algorithms <- list(
  "association rules" = list(name  = "AR", param = list(supp = 0.0001, conf = 0.5)),
  "random items"      = list(name  = "RANDOM",  param = NULL),
  #"popular items"     = list(name  = "POPULAR", param = NULL),
  "item-based CF"     = list(name  = "IBCF", param = list(k = 2))#,
  #"user-based CF"     = list(name  = "UBCF", param = list(method = "Cosine", nn = 500))
)

#results <- evaluate(transact_rs, algorithms, type  = "topNList", n = c(1, 5, 10, 15))
#saveRDS(results, "algorithms.RDS")

results <- readRDS("algorithms.RDS")
```

```{r, echo=FALSE}
avg_conf_matr <- function(results) {
  tmp <- results %>%
    getConfusionMatrix()  %>%  
    as.list() 
    as.data.frame(Reduce("+",tmp) / length(tmp)) %>% 
    mutate(n = c(1, 5, 10, 15)) %>%
    select('n', 'precision', 'recall', 'TPR', 'FPR') 
}
```

```{r, warning=FALSE}
# Using map() to iterate function across all models
results_tbl <- results %>% map(avg_conf_matr) %>% 
# Turning into an unnested tibble
  enframe() %>%
# Unnesting to have all variables on same level
  unnest()
```

#### ROC curve
```{r}
results_tbl %>%
  ggplot(aes(FPR, TPR, 
             colour = fct_reorder2(as.factor(name), 
                      FPR, TPR))) +
  geom_line() +
  geom_label(aes(label = n))  +
  labs(title = "ROC curves", colour = "Model") +
  theme_grey(base_size = 14)
```

```{r}
results_tbl %>%
  ggplot(aes(recall, precision, 
             colour = fct_reorder2(as.factor(name),  
                      precision, recall))) +
  geom_line() +
  geom_label(aes(label = n))  +
  labs(title = "Precision-Recall curves", colour = "Model") +
  theme_grey(base_size = 14)
```


#### Predictions For a New User
```{r}
new_order <- c("APP1215")

kable(line_item_clean %>% filter(sku %in% new_order) %>% select(sku, name_en, short_desc_en, brand, manual_categories) %>% rename(Name = name_en, Description = short_desc_en, Brand = brand, Category = manual_categories) %>% unique() %>% arrange(sku))
```

```{r}
new_order_item_matrx <- line_item_clean %>% 
# Select item descriptions from retail dataset
  select(sku) %>% unique() %>% 
# Add a 'value' column with 1's for customer order items
  mutate(value = as.numeric(sku %in% new_order)) %>% 
# Spread into sparse matrix format
  spread(key = sku, value = value) %>% 
# Change to a matrix
  as.matrix() %>% 
# Convert to recommenderlab class 'binaryRatingsMatrix'
  as("binaryRatingMatrix")
```

```{r}
recomm <- Recommender(getData(transact_rs, 'train'), method = "AR", param = list(supp = 0.0001, conf = 0.5))
```


```{r}
pred <- predict(recomm, newdata = new_order_item_matrx, n = 10)
```

```{r}
kable(line_item_clean %>% filter(sku %in% as(pred, 'list')[[1]]) %>% select(sku, name_en, short_desc_en, brand, manual_categories) %>% rename(Name = name_en, Description = short_desc_en, Brand = brand, Category = manual_categories) %>% unique() %>% arrange(sku))
```

